Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_main_software_credit.tex
Fixed appendix refs in SC main section

A number of groups external to WSSSPE (although with some overlapping members) are also focused on aspects of software credit, including the FORCE11 Software Citation Working Group (see plans for coordination below).
In addition, a Software Credit workshop\footnote{London Software Credit workshop: \url{http://www.software.ac.uk/software-credit}} convened in London on October 19, following the conclusion of WSSSPE3.
See \S\ref{sec:appendix_SW_credit} for more detailed discussion of related activities.

@@

The majority of the remaining discussion focused on standardizing (1) the metadata necessary for software to be cited and (2) the mechanism for citing software in publications.
In addition, discussions also oriented around the indexing of software citations necessary for establishing a software citation network either integrated with the existing paper citation ecosystem or complementary to it.
See \S\ref{sec:appendix_SW_credit} for a more detailed summary of the working group's discussion on these topics.

>>>>

A number of groups external to WSSSPE (although with some overlapping members) are also focused on aspects of software credit, including the FORCE11 Software Citation Working Group (see plans for coordination below).
In addition, a Software Credit workshop\footnote{London Software Credit workshop: \url{http://www.software.ac.uk/software-credit}} convened in London on October 19, following the conclusion of WSSSPE3.
See Appendix~\ref{sec:appendix_SW_credit} for more detailed discussion of related activities.

@@

The majority of the remaining discussion focused on standardizing (1) the metadata necessary for software to be cited and (2) the mechanism for citing software in publications.
In addition, discussions also oriented around the indexing of software citations necessary for establishing a software citation network either integrated with the existing paper citation ecosystem or complementary to it.
See Appendix~\ref{sec:appendix_SW_credit} for a more detailed summary of the working group's discussion on these topics.
